Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-14 paper/ms.tex
Add real clusters to paper

>>>>

We explore one science goal that relies on the conservation of actions --- the
reconstruction of open clusters across large distances using dynamical
tagging. The basic program is to match stars with roughly the same actions. To
set the scene, we consider the orbits of the nine open clusters within
$250\,\pc$ as reported by the {\em Gaia} collaboration
\citep{2018A&A...616A..10G}. In Table~\ref{tab:real_clusters}, we report the
distance to each cluster, the three actions, and the maximum vertical extent
of their orbits ($z_{\text{max}}$). The actions are computed using the
technique described in Section~\ref{ssec:action_comp}.

\begin{deluxetable*}{cccccc}
\tablehead{\colhead{cluster} & \colhead{distance} & \colhead{$J_r$} &
\colhead{$L_z$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$}\\ \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 174.9 & 14.0 & -1739 & 0.0045 & 10.5 \\
Blanco1 & 237.2 & 1.6 & -1841 & 1.53 & 207.0 \\
ComaBer & 85.9 & 1.6 & -1860 & 0.71 & 139.7 \\
Hyades & 47.5 & 20.3 & -1757 & 0.26 & 81.5 \\
IC2391 & 151.6 & 5.5 & -1790 & 0.018 & 21.2 \\
IC2602 & 152.2 & 11.5 & -1718 & 0.32 & 88.6 \\
NGC2451 & 193.7 & 5.8 & -1805 & 0.21 & 73.4 \\
Pleiades & 135.8 & 19.3 & -1696 & 0.38 & 96.3 \\
Praesepe & 186.2 & 21.2 & -1766 & 0.58 & 122.9
\enddata
\tablerefs{\citet{2018AA...616A..10G}}
\label{tab:real_clusters}
\end{deluxetable*}
